\documentclass[acmtog, table, dvipsnames]{acmart}
\usepackage{amsmath}
\usepackage[parfill]{parskip}
\usepackage{hyperref}

\begin{document}
\title{\textbf{Brown CS2240 Final Project Proposal} \\
       Foo}
\author{Tianmu Lan}
\author{Ruolan Tang}
\author{Kai Wang}
\maketitle

\section{Introduction}
We want to make a non-photorealistic render. When you import a 3D model or 3D scene in, you can choose to render it in watercolor style or pencil drawing style. If possible, we want to make it real-time and support some other NPR effects as well.

\section{Features}
\begin{enumerate}
\item watercolor rendering. Shader programming. \cite{montesdeoca2016art}
    \begin{itemize}
	\item Controlled Object-space Effects: color bleeding technique and hand tremors effects.
	\item Watercolor Reflectance Model and Pigment Turbulence.
	\item Controlled Image-space Effects: Edge Darkening, Paper Distortion and Granulation.
    \end{itemize}
\item pencil rendering. \cite{lee2006real} \cite{praun2001real}
    \begin{itemize}
	\item Contour detection and contour shaking.
	\item Multiple contour drawing effects.
	\item Pencil texture generation. 
	\item Pencil texture rotation and 3-way blending.
	\item Compositing and enhancement.
    \end{itemize}
\end{enumerate}

\section{Extensions}
\begin{enumerate}
\item Try using some other methods to implement the watercolor/pencil effect.
\item Try implementing some other stylized NPR effect on our own.
\item Real-time rendering.
\end{enumerate}

\section{Timeline}
1st week (Apr. 7th - 13th): Read paper, build basic framework, set out implementing pencil rendering(finish contour detection and contour shaking).

2nd week (Apr. 14th - 20th): FInish implementing pencil rendering, set out implementing watercolor rendering(finish Controlled Object-space Effects).

3rd week (Apr 21st - 27th): FInish implementing watercolor rendering. Try implementing extension features.

4th week (Apr 28th - May 4th): Debugging, refining. Combine the separate two parts together, make an interface, prepare for presentation.

\section{Division of Labor}
Kai Wang: Multiple contour drawing effects, Pencil texture generation. Watercolor Reflectance Model and Pigment Turbulence. Support real-time rendering.

Ruolan Tang: Contour detection and contour shaking, Compositing and enhancement. Controlled Object-space Effects. UI. Try implementing other NPR effects.

Tianmu Lan: Import and scene parsing. Pencil texture rotation and 3-way blending. Controlled Image-space Effects. Try implementing other NPR effects.

\section{Skills and Expectation}
Kai Wang:

Skills: C++

Predict to Acquire: more in depth knowledge about NPR

Ruolan Tang: 

Skills: C++ and basic graphics knowledge. PBR. Basic shader programming.

Predict to acquire: more in depth knowledge about NPR. Advanced shader programming abilities. More practice on paper implementation .

Tianmu Lan:

Skills: C++ and basic shader implementation.

Predict to acquire: more knowledge about shader implementation and more practice on paper implementation .

\bibliographystyle{ACM-Reference-Format}
\bibliography{main}

\end{document}

